\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-18 doc/flexiblesusy-paper.tex
update my address
slightly reformulate SLHA compatibility with decay calulators

\author[adelaide]{Peter Athron}
\author[valencia]{Jae-hyeon Park}
\author[dresden]{Dominik St\"ockinger}
\author[dresden]{Alexander Voigt\corref{cor1}}
\ead{Alexander.Voigt@physik.tu-dresden.de}
\cortext[cor1]{Corresponding author}
\address[adelaide]{ARC Centre of Excellence for Particle Physics at 
the Tera-scale, School of Chemistry and Physics, University of Adelaide, 
Adelaide SA 5005 Australia}
\address[valencia]{Departament de F\'{i}sica Te\`{o}rica and IFIC,
Universitat de Val\`{e}ncia-CSIC,
46100, Burjassot, Spain}
\address[dresden]{Institut f\"ur Kern- und Teilchenphysik,
TU Dresden, Zellescher Weg 19, 01069 Dresden, Germany}

@@

The standard input and output of the generated code is given in
SLHA-style format where the user has control of the Block names by
editing the SARAH files and may also add extra blocks in the
FlexibleSUSY.m model file which is decribed in section 5. We use
SLHAea \cite{slhaea} to create these SLHA files and with a simple
modifications these can be passed directly to another code which uses
them as an alternative to writing out the SLHA file. Since the SLHA
standard is intended precisely for the purpose, MSSM and NMSSM codes
should be compliant with this.  We have tested that the versions of
HDECAY\cite{hdecay} and SDECAY\cite{sdecay} inside SUSY-HIT
\cite{susyhit} can understand the SLHA output of FlexibleSUSY and give
matching output to that from SOFTSUSY.

>>>>

\author[adelaide]{Peter Athron}
\author[valencia]{Jae-hyeon Park}
\author[dresden]{Dominik St\"ockinger}
\author[desy]{Alexander Voigt\corref{cor1}}
\ead{Alexander.Voigt@desy.de}
\cortext[cor1]{Corresponding author}
\address[adelaide]{ARC Centre of Excellence for Particle Physics at 
the Tera-scale, School of Chemistry and Physics, University of Adelaide, 
Adelaide SA 5005 Australia}
\address[valencia]{Departament de F\'{i}sica Te\`{o}rica and IFIC,
Universitat de Val\`{e}ncia-CSIC,
46100, Burjassot, Spain}
\address[dresden]{Institut f\"ur Kern- und Teilchenphysik,
TU Dresden, Zellescher Weg 19, 01069 Dresden, Germany}
\address[desy]{Deutsches Elektronen-Synchrotron (DESY), 22607 Hamburg, Germany}

@@

The standard input and output of the generated spectrum generator is
the SLHA format \cite{Skands:2003cj,Allanach:2008qq}, which is
intended for the communication between MSSM and NMSSM spectrum
generators and observable calculators.  The user has control over the
SLHA block names by editing the SARAH model files and may also add
extra blocks in the \code{FlexibleSUSY.m} model file, as described in
\secref{sec:modfile}.
%
% We use SLHAea \cite{slhaea} to create these SLHA files and with
% simple modifications these can be passed directly to another code
% which uses them as an alternative to writing out the SLHA file.
%
We have tested that the HDECAY $3.4$ \cite{hdecay} and SDECAY $1.4$
\cite{sdecay}, which are shipped with SUSY-HIT \cite{susyhit},
understand the SLHA output of \fs and give matching output to that
from Softsusy.
